A Comparison of the Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-06-28 mt-marathon.2012/PBML_article.tex
from google doc
blah blah blah

\institute{label1}{University of Edinburgh}
\institute{label2}{Center for Language and Speech Processing, Johns Hopkins University}
\institute{label3}{Carnegie Mellon University}

\author{
  firstname=Hieu,
  surname=Hoang,
  institute=label1,
}
\author{
  firstname=Matt,
  surname=Post,
  institute=label2,
}
\author{
  firstname=Chris,
  surname=Dyer,
  institute=label3,
}
\author{
  firstname=Eva,
  surname=Hasler,
  institute=label1,
}
\author{
  firstname=Barry,
  surname=Haddow,
  institute=label1,
}
\author{
  firstname=Philipp,
  surname=Koehn,
  institute=label1,
}

@@

% The title and authors' names are used in the running head. If they are
% long, you should define short versions. These definitions are optional. You
% define them only if they are needed. The example follows:
\shorttitle{Short title}
\shortauthor{H. Dumpty, M. Turtle, C. Cat}

@@

\subsection{Moses}
Moses explicitly implements both dense and sparse features, and each score must be identifiable as one or the other.
The intuition behind this is that most systems will still contain dense features, with a smattering of sparse features. Therefore, it would be more efficient to use dedicated

>>>>

\institute{label1}{University of Edinburgh}
\institute{label2}{Center for Language and Speech Processing, Johns Hopkins University}
%\institute{label3}{Carnegie Mellon University}

\author{
  firstname=Hieu,
  surname=Hoang,
  institute=label1,
}
\author{
  firstname=Matt,
  surname=Post,
  institute=label2,
}
\author{
  firstname=Kenneth,
  surname=Heafield,
  institute=label1,
}
%\author{
%  firstname=Chris,
%  surname=Dyer,
%  institute=label3,
%}
\author{
  firstname=Eva,
  surname=Hasler,
  institute=label1,
}
\author{
  firstname=Phil,
  surname=Williams,
  institute=label1,
}
\author{
  firstname=Barry,
  surname=Haddow,
  institute=label1,
}
\author{
  firstname=Philipp,
  surname=Koehn,
  institute=label1,
}

@@

% The title and authors' names are used in the running head. If they are
% long, you should define short versions. These definitions are optional. You
% define them only if they are needed. The example follows:
\shorttitle{SCFG Decoder Implementations}
\shortauthor{H. Dumpty, M. Turtle, C. Cat}

@@

\subsection{Moses}
Moses explicitly implements both dense and sparse features, and each score must be identifiable as one or the other.
The intuition behind this is that most systems will still contain dense features. Therefore, it would be more efficient to use dedicated dense vectors for these scores.

A sparse feature map was added to handle sparse scores.

\subsection{CDEC}
CDEC eschew the dense and sparse hybrid approach and implement only sparse maps. Dense features can still be modelled in the framework, with some loss of efficiency.

To improve speed and memory usage, hypotheses only store deltas of sparse features differences with antecedent hypotheses.

\subsection{Joshua}
As with CDEC, Joshua only supports sparse features, however, it uses a different tack to improve efficiency.

Hypotheses only retain the weighted sum of the feature scores. They do not retain the individual score components unless required, for example, in the n-best list. The intuition behind this approach is that the score breakdown is only required in some situations such as producing n-best lists for tuning. In most other circumstances, they can be traded for better performance.
